Capital Budget Funding in Toronto

### 2024-09-25 paper/paper.qmd
wrote about the data sources used

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

@@

Our results are summarized in @tbl-modelresults.

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

Weaknesses and next steps should also be included.

>>>>

## Data Sources

This research utilized two primary datasets provided by the City of Toronto's Open Data Portal.

1.  Capital Budget & Plan By Ward (2022-2031): \\
This dataset contains the approved capital budget and plan for each of Toronto's 25 wards over a ten-year period from 2022 to 2031. It includes funding allocations for various programs such as Children's Services, Parks, Foresty & Recreation, Transportation Services, and others. The data provides a detailed breakdown of how much funding each ward is set to receive for specific projects and services.

2.  Ward Profiles (2021): \\
This dataset provides comprehensive socioeconomic information for each ward based on the 2021 census. It was filtered to remain the variables which were most useful for this research. These are: Total Population, Median Household Income, Prevalence of Low Income Households, Educational Attainment, Immigration Status, Visible Minority Population. [may need to include others, depends on what I decide to go with in the end.]

@@

Lots of tables and graphs to be included here once they're properly formatted!

@@

@@
